White Dwarf Mergers on Adaptive Meshes\\ II. Collisions

### 2016-07-12 papers/wdmerger_II/paper.tex
Correct some wording in an explanation

In contrast, the suppressed burning mode (modelled after \citet{kushnir:2013}) produces only about
$5 \times 10^{-4}\ \msolar$ of $^{56}$Ni. In a suppressed burn, we ensure that at every evaluation
of the right-hand-side vector for the nuclear network integration, all quantities are scaled by the
same factor, with this factor ensuring that the energy release is not large enough to permit a
spurious detonation. This seems to be equivalent to the method used in \citet{kushnir:2013}. Yet
we do not reproduce their claim that this fix is sufficient to ensure that the detonation occurs
at the proper and time and place; indeed, the burning is quenched until very late in the collision,
and the detonation barely forms at all. The suppression used therefore seems to be far too strong
to permit an actual detonation when one should occur. We have also checked the same method at higher
resolution and found that the nickel produced is significantly smaller than for a self-heating
calculation at the same resolution.

>>>>

In contrast, the suppressed burning mode (modelled after \citet{kushnir:2013}) produces only about
$5 \times 10^{-4}\ \msolar$ of $^{56}$Ni. In a suppressed burn, we ensure that at every evaluation
of the right-hand-side vector for the nuclear network integration, all quantities are scaled by the
same factor, with this factor ensuring that the energy release is not large enough to permit a
spurious detonation. This seems to be equivalent to the method used in \citet{kushnir:2013}. We
reproduce their claim that this suppresses the detonation until later in the collision, after more
material has approached the stalled shock. We also observe that, for a given resolution, the simultaneous
detonations occur slightly outside the initial contact point, near the edges of the stalled shock. They
establish as the main source of error in simulations that produce too little nickel. However, we find
that the resulting detonations are not strong enough to convert a significant amount of material to NSE
conditions; instead, only QSE conditions are reached near the center of the collision, leaving a significant
amount of silicon and sulfur on the domain that is not further processed.
